General writeup

### 2018-09-12 Latex/Poster_Session/poster_session.tex
tiny change in poster
poster update

\begin{minipage}[b]{0.55\linewidth}
\veryHuge \color{NavyBlue} \textbf{ICT and Future Productivity} \color{Black}\\ % Title
\Huge\textit{Evidence and Theory of a GPT}\\[1cm] % Subtitle
\huge \textbf{Marco Brianti \& Laura Gati}\\ % Author(s)
\huge Boston College\\ % University/organization
\end{minipage}
%
\begin{minipage}[b]{0.25\linewidth}
\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
Department of Economics\\ % Address
Boston College\\
140 Commonwealth Avenue, Chestnut Hill, MA \\\\
Phone: +1 (617) 552 3670\\ % Phone number
Email: \texttt{brianti@bc.edu, gati@bc.edu}\\ % Email address
\end{minipage}
%
\begin{minipage}[b]{0.19\linewidth}
\includegraphics[width=25cm]{logo.jpg} % Logo or a photo of you, adjust its dimensions here
\end{minipage}

@@

In response to this shock, ICTI rises on impact and remains significant for several quarters. RP persistently and significantly declines for more than two years, suggesting that we are indeed identifying the correct sectoral shock. Our main result is that TFP, restricted not to respond on impact, rises after few quarters and remains significant and stable for at least 5 years, despite the tiny size of the ICT sector relative to the economy. Finally, variance decomposition analysis suggests that ICT shocks explain a remarkable size of economic fluctuations over the medium and long run. These shocks drive about $40$\% and $33$\% of the overall GDP and TFP fluctuations over a 10-year horizon, respectively.

>>>>

\begin{minipage}[b]{0.55\linewidth}
\veryHuge \color{NavyBlue} \textbf{ICT-Specific Investment Shocks and Economic  \\ Fluctuations} \color{Black}\\ % Title
\Huge\textit{Evidence and Theory of a General-Purpose Technology}\\[1cm] % Subtitle
\huge \textbf{Marco Brianti \& Laura G\'ati}\\ % Author(s)
\huge Boston College\\ % University/organization
\end{minipage}
%
\begin{minipage}[b]{0.25\linewidth}
\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
Department of Economics\\ % Address
Boston College\\
140 Commonwealth Avenue, Chestnut Hill, MA \\\\
Phone: +1 (617) 552 3670\\ % Phone number
Email: \texttt{brianti@bc.edu, gati@bc.edu}\\ % Email address
\end{minipage}
%
\begin{minipage}[b]{0.19\linewidth}
\includegraphics[width=25cm]{logo.jpg} % Logo or a photo of you, adjust its dimensions here
\end{minipage}

@@

In response to the ICT shock, ICTI rises on impact and remains significant for several quarters. RP persistently and significantly declines for more than two years, suggesting that we are indeed identifying the correct sectoral shock. Our main result is that TFP, restricted not to respond on impact, rises after few quarters and remains significant and stable for at least 5 years, despite the tiny size of the ICT sector relative to the economy. Finally, variance decomposition analysis suggests that ICT shocks explain a remarkable size of economic fluctuations over the medium and long run. These shocks drive about $40$\% and $33$\% of the overall GDP and TFP fluctuations over a 10-year horizon, respectively.
